How to use replication assignments for teaching integrity in empirical archaeology

### 2019-06-21 analysis/paper/paper.Rmd
add edits from Ryan

To enable re-use of our materials and improve reproducibility and transparency according to the principles outlined in @marwick2017open, we include all our assingment materials, as well as the entire R code used for all the analysis and visualizations contained in this paper, in our compendium at http://doi.org/10.17605/OSF.IO/DBSW9. Also in this version-controlled compendium are the raw data for the analyses reported here. The figures and results presented here can be independently reproduced with the code and data in this repository. In our compendium our code is released under the MIT licence, our data as CC-0, and our figures and assingment materials as CC-BY, to enable maximum re-use [for more details, see @Marwick2017].

@@

Some of the earliest discussions of replication in university curricula appear in economics and psychology [@hoffler2013teaching; @standing2014using]. @Ball_Medeiros_2012 describe their TIER (teaching integrity in empirical research) protocol for undergraduate economics students at Haverford College. This is intended to ensure that a student's work is replicable by the instructors. Their protocol requires that when students submit their final project report, their submission must contain four elements: the raw data files, a metadata file, script files of code used to analyse the data, and public availability (i.e. deposit on an open repository such as Dataverse). @frank2012teaching describe how they teach undergraduates (at MIT) and graduate students (at Stanford) to do in-class replications of recent, cutting-edge psychology experiments, and note that several projects from their undergraduate course have even been part of successful publications. More recently @hawkins2018improving reported on 11 replication assignments from a psychology graduate seminar at Stanford, finding that the replications typically yielded effects that were smaller than the originally published ones. Similarly, @jern2018preliminary describes how students in a psychology course completed replication assignments by using statistical methods of the original research articles with new data collected by the students outside of class.

@@

The challenges of requiring students to do replication assignments are similar to those faced in many types of archaeology classes with quantitative skills at their core. In our case, the absence of a prerequisite and the high variability of statistical and programming skills meant that some students needed a lot more support than others. This may make replication assignments impractical where instructor-student contact hours are limited. In addition to time, the instructor needs to have a high skill level in quantitative methods to guide students in their engagement with the literature. The instructor will also benefit from a high tolerance for helping students to solve coding problems. To mitigate this in the future we will add a step of student peer review to distribute the feedback task beyond the instructor and give students an opporutnity to get assistance from each other more formally.

>>>>

To enable re-use of our materials and improve reproducibility and transparency according to the principles outlined in @marwick2017open, we include all our assignment materials, as well as the entire R code used for all the analysis and visualizations contained in this paper, in our compendium at http://doi.org/10.17605/OSF.IO/DBSW9. Also in this version-controlled compendium are the raw data for the analyses reported here. The figures and results presented here can be independently reproduced with the code and data in this repository. In our compendium our code is released under the MIT licence, our data as CC-0, and our figures and assignment materials as CC-BY, to enable maximum re-use [for more details, see @Marwick2017].

@@

Some of the earliest discussions of replication in university curricula appear in economics and psychology [@hoffler2013teaching; @standing2014using]. @Ball_Medeiros_2012 describe their TIER (Teaching Integrity in Empirical Research) protocol for undergraduate economics students at Haverford College. This is intended to ensure that a student's work is replicable by the instructors. Their protocol requires that when students submit their final project report, their submission must contain four elements: the raw data files, a metadata file, script files of code used to analyse the data, and public availability (i.e. deposit on an open repository such as Dataverse). @frank2012teaching describe how they teach undergraduates (at MIT) and graduate students (at Stanford) to do in-class replications of recent, cutting-edge psychology experiments, and note that several projects from their undergraduate course have even been part of successful publications. More recently @hawkins2018improving reported on 11 replication assignments from a psychology graduate seminar at Stanford, finding that the replications typically yielded effects that were smaller than the originally published ones. Similarly, @jern2018preliminary describes how students in a psychology course completed replication assignments by using statistical methods of the original research articles with new data collected by the students outside of class.

@@

The challenges of requiring students to do replication assignments are similar to those faced in many types of archaeology classes with quantitative skills at their core. In our case, the absence of a prerequisite and the high variability of statistical and programming skills meant that some students needed a lot more support than others. This may make replication assignments impractical where instructor-student contact hours are limited. In addition to time, the instructor needs to have a high skill level in quantitative methods to guide students in their engagement with the literature. The instructor will also benefit from a high tolerance for helping students to solve coding problems. To mitigate this in the future we will add a step of student peer review to distribute the feedback task beyond the instructor and give students an opportunity to get assistance from each other more formally.
